\section*{\centering ACKNOWLEDGMENTS}
The success of a project requires help and contribution from numerous individuals and 
the organization. Writing the report of this project work gives me an opportunity to 
express my gratitude to everyone who has helped in shaping up the final outcome of my 
project work.
 \paragraph{} I express my heartfelt gratitude to my project guide {\bf Dr. M. S. Bhat.} for 
giving me an opportunity to do my major project work under his guidance. His constant 
support and encouragement has made me realize that it is the process of learning which 
weighs more than the end result.

\paragraph{}I am highly indebted to my external guide, {\bf Mr. Narendran Kumaragurunathan}, Senior Member Technical Staff, AMD India Pvt Ltd, for
his guidance, constant supervision and for motivating me to complete my work.
He helped me throughout by giving new ideas, providing necessary information and
pushing me forward to finish the project work. 

\paragraph{} Many thanks to {\bf Dr. John D'Souza}, M.Tech Project Co-coordinator, Department of 
Electronics and Communication, for his valuable suggestions and help.
\paragraph{} I would like to thank all the team members of SoC Verification Team at AMD India Pvt Ltd, Bangalore for their support and help through out the course of my work there.
\paragraph{} My deep gratitude to my family and friends who have stood by me at all times, motivating 
me and bearing my mood swings. Many thanks to all who have helped me, directly or indirectly, in 
the successful completion of my project work
%has helped me push myself through rough times.
