\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@rmstyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand\BIBentrySTDinterwordspacing{\spaceskip=0pt\relax}
\providecommand\BIBentryALTinterwordstretchfactor{4}
\providecommand\BIBentryALTinterwordspacing{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand\BIBforeignlanguage[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\bibitem{soc}
Mosensoson, Guy,``Practical approaches to SoC verification.''\emph{In Proceedings of DATE User Forum,} pp. 05-08. 2002.

\bibitem{phd:zhang}
Zhang, L. (2005),`` Design Verification for Sequential Systems at Various Abstraction Levels,''\emph{Doctoral dissertation, Virginia Polytechnic Institute and State University,}2005.

\bibitem{ieee:formal:2004}
Tasiran, Serdar, Yuan Yu, and Brannon Batson,``Linking simulation with formal verification at a higher level,''\emph{Design & Test of Computers,} IEEE 21, no. 6, pp. 472-482,2004.

\bibitem{SS:AMD64-V1}
\BIBentryALTinterwordspacing
AMD Corporation (May 2011). ``Volume 1: Application Programming''. \emph{AMD64 Architecture Programmer's Manual}. AMD Corporation. Retrieved 2011-10-29.
\url{http://support.amd.com/us/Processor_TechDocs/24592_APM_v1.pdf}
\BIBentrySTDinterwordspacing
 
\bibitem{SS:AMD64-V2}
\BIBentryALTinterwordspacing
AMD Corporation (May 2011). ``Volume 2: System Programming''. \emph{AMD64 Architecture Programmer's Manual}. AMD Corporation. Retrieved 2011-10-29.
\url{http://support.amd.com/us/Embedded_TechDocs/24593.pdf}
\BIBentrySTDinterwordspacing
 
\bibitem{http:dygraphs}
\BIBentryALTinterwordspacing
Dygraphs. (2013, Jun.) {JavaScript Visualization Ligrary}. [Online]. Available:
  \url{http://dygraphs.com/}
\BIBentrySTDinterwordspacing


\bibitem{ieee:segev:2004}
Segev, Eyal, Sharon Goldshlager, Hillel Miller, Oren Shua, Olga Sher, and Shlomo Greenberg,``Evaluating and comparing simulation verification vs. formal verification approach on block level design,'' \emph{In Electronics, Circuits and Systems, 2004. ICECS 2004. Proceedings of the 2004 11th IEEE International Conference},pp. 515-518, 2004.


\bibitem{ieee:power:2009}
Zhang,~Y., & Zhang,~G. ``Fast gate-level simulation and power analysis for high performance microprocessor,'' in {\emph IEEE Computer Science & Education, 2009. ICCSE'09. 4th International Conference}, pp. 1155-1158, 2009.


\bibitem{ieee:v:2005}
  IEEE,
  \emph{``1364-2005 - IEEE Standard for Verilog Hardware Description
  Language''}.
	IEEE STANDARD,
	2005

\bibitem{ieee:sv:2009}
  IEEE,
	\emph{``1800-2012 - IEEE Standard for SystemVerilog--Unified Hardware Design,
  Specification, and Verification Language''}.
	IEEE STANDARD,
	2009

\bibitem{ieee:boolean}
Randal E. Bryant,
  ``Graph-Based Algorithms for Boolean Function Manipulation,'' \emph{IEEE Transactions on Computers}, vol.C ~35, no.~12, 1986.

\bibitem{lec}
McDonald, William, and Janny Liao,
	``Logic Equivalence Checking Has Arrived For FPGA Developers.`` \emph{Design and Verification Conference (DVCon)}, 2006.

\bibitem{SS:Verdi}
\BIBentryALTinterwordspacing
SpringSoft. (2013, May.) {Verdi Automated Debug System}. [Online]. Available:
  \url{http://www.springsoft.com/products/debug-automation/verdi}
\BIBentrySTDinterwordspacing

	
%\bibitem{compton2002reconfigurable}
%K.~Compton and S.~Hauck, ``Reconfigurable computing: a survey of systems and
%  software,'' \emph{ACM Computing Surveys (csuR)}, vol.~34, no.~2, pp.
%  171--210, 2002.
%
%\bibitem{P1171121623}
%M.~Ramesh~Kini and S.~Sumam~David, ``Asic implementation of address generation
%  unit for digital signal processing kernel-processor,'' \emph{ICGST
%  International Journal on Programmable Devices, Circuits and Systems, PDCS},
%  vol.~11, pp. 1--9, December 2011.
%
%\bibitem{graham1999reconfigurable}
%P.~Graham and B.~Nelson, ``Reconfigurable processors for high-performance,
%  embedded digital signal processing,'' in \emph{Proceedings of 9th
%  international workshop on Field Programmable Logic and Applications}.\hskip
%  1em plus 0.5em minus 0.4em\relax Springer, 1999, pp. 1--10.
%
%\bibitem{ramesh2009comprehensive}
%M.~Ramesh~Kini and S.~Sumam~David, ``Comprehensive address generator for
%  digital signal processing,'' in \emph{Proceedings of International Conference
%  on Industrial and Information Systems (ICIIS 2009),Srilanka}.\hskip 1em plus
%  0.5em minus 0.4em\relax IEEE, 2009, pp. 325--330.
%
%\bibitem{huang2002reconfigurable}
%Z.~Huang and S.~Malik, ``Exploiting operation level parallelism through
%  dynamically reconfigurable datapaths,'' in \emph{Proceedings of the 39th
%  annual Design Automation Conference}.\hskip 1em plus 0.5em minus 0.4em\relax
%  ACM, 2002, pp. 337--342.
%
%\bibitem{SS:AMD64}
%\BIBentryALTinterwordspacing
%AMD64 Architecture Programmer's Manual Volume 1: Application Programming (2005, Nov)
%\url{http://www.serc.iisc.ernet.in/facilities/ComputingFacilities/systems/tyrone/Application\%20Programming.pdf}
%\BIBentrySTDinterwordspacing
\bibitem{SS:Cadence}
\BIBentryALTinterwordspacing
Cadence. (2013, Jan.) {Functional Verification Survey-{\emph Why Gate-Level Simulation is Increasing}}.[Online]. Available:
\url {http://www.cadence.com/Community/blogs}
\BIBentrySTDinterwordspacing

\bibitem{SS:Cadence-2}
\BIBentryALTinterwordspacing
Cadence. (2012, Jan.) {Gate-Level Simulation Methodology-{\emph Improving Gate-Level Simulation Performance}}.[Online]. Available:
\url {http://www.cadence.com/rl/Resources/white_papers/Gate_Level_Simulation_WP.pdf}
\BIBentrySTDinterwordspacing


\bibitem{Verdi:FsdbReader}
\BIBentryALTinterwordspacing
Novas. (2011, Oct.) [Tool Installation Resources]. Available:
  \verb|$VERDI_HOME/share/FsdbReader/doc/FsdbReader.pdf|
\BIBentrySTDinterwordspacing

\bibitem{VCS:vcs.pdf}
\BIBentryALTinterwordspacing
Synopsys. (2013, Dec.) [Tool Installation Resources]. Available:
  \verb|$VCS_HOME/doc/UserGuide/pdf/vcs.pdf|
\BIBentrySTDinterwordspacing

\bibitem{wiki:2013:VPI}
\BIBentryALTinterwordspacing
Wikipedia. (2013, June.) {Verilog Procedural Interface}. [Online]. Available:
  \url{http://en.wikipedia.org/wiki/Verilog_Procedural_Interface}
\BIBentrySTDinterwordspacing

\bibitem{aw:2013:VPI}
\BIBentryALTinterwordspacing
Asic World. (2013, June.) {Verilog Procedural Interface}. [Online]. Available:
  \url{http://www.asic-world.com/verilog/pli6.html}
\BIBentrySTDinterwordspacing

\bibitem{aw:2013:vbooks}
\BIBentryALTinterwordspacing
Asic World. (2013, June.) {Verilog Books}. [Online]. Available:
  \url{http://www.asic-world.com/verilog/books.html}
\BIBentrySTDinterwordspacing

\bibitem{ss:pli:1999}
\BIBentryALTinterwordspacing
Sutherland, Stuart.  {\em The Verilog PLI Handbook: A User's Guide and Comprehensive
  Reference on the Verilog Programming Language Interface}.
\newblock Springer, 1999. Hardcover.
\newblock ISBN: 0-7923-8489-X.
\BIBentrySTDinterwordspacing

\bibitem{sm:pli:1999}
\BIBentryALTinterwordspacing
Mittra, Swapnajit.  {\em Principles of Verilog PLI}.
\newblock Springer, 1999. Hardcover.
\newblock ISBN: 0-7923-8477-6
\BIBentrySTDinterwordspacing

%\bibitem{tms320c55x2001programmer}
%T.~DSP, ``Programmer’s guide,'' \emph{SPRU376, Texas Instruments}, 2001.
%
%\bibitem{EDKconceptsUG683}
%Xilinx, ``Edk concepts, tools, and techniques,'' \emph{UG683 (v12.3), Xilinx},
%  Sept. 2010.
%
%\bibitem{chipscopeguideUG029}
%Xilinx, ``Chipscope pro 12.1 software and cores,'' \emph{UG029 (v12.1),
%  Xilinx}, Apr. 2010.
%
%\bibitem{dorairaj2005planahead}
%N.~Dorairaj, E.~Shiflet, and M.~Goosman, ``Planahead software as a platform for
%  partial reconfiguration,'' \emph{Xcell Journal}, vol.~55, pp. 68--71, 2005.
%
%\bibitem{oslibref}
%Xilinx, ``Xilinx OS and Libraries document collection,'' \emph{UG643, Xilinx},
%  April. 2012.

\end{thebibliography}
